### 2020-09-23 LaTeX/sections/paper.tex
appendix
full round edit (#2)

\paragraph{Execution systems.} There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses their own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.

@@

\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution. Security breaches and fraud (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) in centralized exchanges have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.

@@

In this paper, we focus on benchmarking an order book for a public blockchain (\eg Ethereum). Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is good lower-bound). Exchanges could be given their own dedicated blockchain, where trade execution logic can be moved at the consensus level. Permissioned blockchains (\eg NASDAQ Linq, tZero) can also increase execution time and throughput, possibly with some reduction in transparency and trust.

\paragraph{On-chain Dealers.} Another on-chain advantage is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long term profit through trading fees. By contrast, an order book requires no upfront inventory and does not have to charge trading fees (but can). Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.

\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality. Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist: many avoiding taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain. A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair. A mitigation is to issue a proof of correct execution to the DApp (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}). \cm offers key advantages in this model as well.

@@

\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain. An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work. The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancelations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).

@@

Large exchanges, like the NYSE and NASDAQ, use a two minute call market every day at opening and closing time (in between, the exchange runs as a continuous time market). Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `	dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks. In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled. The only exceptions are in the case of a tie on price or a canceled order, both of which we return to later. For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price. Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.

@@

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implemented a priority queue with a heap that stores its data in a dynamically-sized array.

@@

\subsubsection{Enqueue performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance. A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}. We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant. The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\textwidth]{fig/random_insertion2.png}
\caption{\footnotesize{Gas costs for enqueuing random integers into five priority queue variants. For the x-axis, a value of 10 indicates it is the 10th number entered in the priority queue. The y-axis is the cost of enqueue in gas.}  \label{fig:random_insertion}}
\end{figure}

@@

\subsubsection{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are cheapest. This is in accordance with the theoretical worst-case time complexity for each. However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor. For these reasons, we suggest using a linked list variant for this specific application. As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new contract. Accordingly, we choose to implement the call market with the linked list with mapping. Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).

@@

\subsection{Cost/Benefit of cleaning up after yourself}
\label{sec:gasrefund}

@@

One consequence of a linked list is that a new contract is created for every node in the list. Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.'). However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function. As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.  This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds. Unfortunately, this is not universally true as shown by applying the same principle to the linked list with mapping.

Dequeuing in a linked list with mapping can be implemented in two ways. The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again). Alternatively we can call \texttt{DELETE} on each mapping entry once we are done with a node in the PQ. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}. As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some clean up and we select linked list with mapping and \texttt{DELETE} for \cm.

@@

\cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions. A call market will open for a specified period of time during which it will accept orders. Orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). We keep the design simple by not allowing cancellations. Because markets are relatively short-lived, cancelations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}, orders simply expire when the market call period ends.

@@

The main research question is how many orders can be processed in a single Ethereum transaction when the closing the call market, using Ethereum today. As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determined the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column. The fourth column indicates the cost to the trader of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

@@

\paragraph{Code Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net} on \cm to find vulnerabilities and bad practices across 67 tests. \cm passes all test except some `informational' warnings (\eg a costly loop) that are intentional design choices.

\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.

Potential for front-running still exists around ties on price and cancelations (see below). Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them. In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement. A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price from their order---and it removes any incentive to front-run these profits. For all these reasons, we say \cm reduces front-running attacks but stop short of saying it is completely solved by \cm.

@@

As a module, we try to keep \cm as simple as possible, and allow customization and extensions as appropriate. We discuss potential modifications here.

@@

\subsection{Cancellations}

\cm does not support order cancelations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived. Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes). Finally, cancellations have a performance impact. Cancelled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

@@

A close alternative is to allow markets to open and close on different blocks. Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.

@@

It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself. However we consider two other (more realistic) scenarios. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty). Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. The fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).

@@

We implement a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain. Anyone capable of running EVM code can verify the result. If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made. With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.

@@

Our \cm variant is not the first rollup-based order book. Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous time order book. The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant requires on-chain submission. While on-chain submission is hampered by Ethereum's block limits, the threat model of reordering transactions is well-understood and our call market design mitigates most front-running attacks. In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous time order book. In short, we provide better protection against a malicious exchange while Loopring 3.0 provides even better performance.

%% = = = = = = = = = = = =Transferring the Collateral back to the traders = = = = = = = = = = = = =  %
%\subsection{Collateralization}
%
%Options for non-collateralized markets
%ERC20 to ERC20 -> extra transaction
%

>>>>

\paragraph{Execution Systems.} There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch like an auction.

@@

\paragraph{Central Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, and offering the best possible price execution. Security breaches and fraud (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) in centralized exchanges have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove.

@@

In this paper, we focus on benchmarking an order book for a public blockchain (\eg Ethereum). Ethereum is widely-used and we stand to learn the most from working in a performance-hostile environment (\ie Ethereum is a good lower-bound). Exchanges could be given their own dedicated blockchain, where trade execution logic can be moved at the consensus level. Permissioned blockchains (\eg NASDAQ Linq, tZero) can also increase execution time and throughput, possibly with some reduction in transparency and trust.

\paragraph{On-chain Dealers.} Another on-chain advantage is that other smart contracts, not just human users, can initiate trades, enabling broader decentralized finance (DeFi) applications. This has fuelled a resurgence in on-chain exchange but through a quote-driven design rather than an order-driven one. Automated market makers  (\eg Uniswap) have all the trust advantages of an on-chain order book, plus they are very efficient relative to an on-chain order book. The trade-off is that they operate as a dealer---the DApp exchanges assets from its own inventory. This inventory is loaded into the DApp by an investor who will not make money on the trades themselves, but hope for long-term profit through trading fees. By contrast, an order book requires no upfront inventory and does not have to charge trading fees (but can). Finally, there is a complicated difference in their price dynamics (\eg market impact of a trade, slippage between the best bid/ask and actual average execution price, \etc)---deserving of an entire research paper to precisely define. We leave it as an assertion that with equal liquidity, order books have more favourable price dynamics for traders.

\paragraph{Hybrid Designs.} Before on-chain dealers became prominent in the late 2010s, the most popular design was hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionality. Some (\eg EtherDelta) were envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist: many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain. A non-custodial DEX solves the big issue of a CEX---the operator stealing the funds---however trade execution is still not provably fair. A mitigation is to issue a proof of correct execution to the DApp (\eg Loopring) but these proofs have blindspots (discussed in section~\ref{sec:rollups}). \cm offers key advantages in this model as well.

@@

\paragraph{Blockchain Limitations and Solution.} While an order book is a ledger and blockchains provide a distributed ledger, it is not straightforward to drop a continuous-time order book onto a blockchain. An older 2014 paper~\cite{clark2014decentralizing} on the `Princeton prediction market'~\cite{Bra13} motivates our work. The authors observe the following limitations of on-chain continuous order books: block intervals are slow and not continuous, there is no support for accurate time-stamping, transactions can be dropped or reordered by miners, fast traders can react to submitted orders/cancellations when broadcast to network but not in a block and have their orders appear first (as examined in later work on front-running: \cite{eskandari2019sok,daian2019flash}).

@@

Large exchanges, like the NYSE and NASDAQ, use a two minute call market every day at opening and closing time (in between, the exchange runs as a continuous-time market). Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call market are studied widely in finance~\cite{Har03}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

When closing a call market, the orders are examined in order: highest to lowest price for bids, and lowest to highest price for asks. In most circumstances, the market closing algorithm does not have to consider any deeper bids/asks from the list when choosing whether the current best bid and ask can be fulfilled. The only exceptions are in the case of a tie on price or a cancelled order, both of which we return to later. For this reason, the ideal data structure for storing bids/asks is a \textit{priority queue} (see Table~\ref{tab:PQ_API}) where each order's priority is its price. Specifically, we use two PQs---one for bids where the highest price is the highest priority, and one for asks where the lowest price is the highest priority.

@@

\item \textbf{Heap with Dynamic Array.} A heap is a type of binary tree data structure that comes in two forms of a (i) Max-Heap and (ii) Min-Heap. All the nodes of the tree are in a specific order and the root always represents the highest priority item of the data structure (the largest and smallest values in the Max-Heap and Min-Heap respectively). We implement a priority queue with a heap that stores its data in a dynamically-sized array.

@@

\subsubsection{Enqueue Performance.} We implemented, deployed, and tested each priority queue using Truffle and Ganache.\footnote{Github: Link removed for anonymity.} We tried a variety of tests (including testing the full call market with each variant) with consistent results in performance. A simple test to showcase the performance profile is shown in Figure~\ref{fig:random_insertion}. We simply enqueue 50 integers chosen at random from a fixed interval in each PQ variant. The bigger the PQ gets, the longer enqueue takes---a linear increase for the linked list variants, and logarithmic for the heap variants.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\textwidth]{fig/random_insertion2.png}
\caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants. For the x-axis, a value of 9 indicates it is the 9th number entered in the priority queue. The y-axis is the cost of enqueuing in gas.}  \label{fig:random_insertion}}
\end{figure}

@@

\subsubsection{Discussion.} Based on enqueuing, the heap variants are the cheapest in terms of gas, while based on dequeuing, the link list variants are the cheapest. This is in accordance with the theoretical worst-case time complexity for each. However, (i) the linked list variants are materially cheaper than the heap variants at dequeuing, and (ii) dequeuing in a call market must be done as a batch, whereas enqueuing is paid for one at a time by the trader submitting the order, and (iii) Ethereum will not permit more than hundreds of orders so the asymptotic behaviour is not a significant factor. For these reasons, we suggest using a linked list variant for this specific application. As it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into a linked list PQ is significantly greater than the linked list with mapping, as each insertion causes the creation of a new contract. Accordingly, we choose to implement the call market with the linked list with mapping. Overall this PQ balances a moderate gas cost for insertion (\ie order submission) with one for removal (\ie matching the orders).

@@

\subsection{Cost/Benefit of Cleaning up After Yourself}
\label{sec:gasrefund}

@@

One consequence of a linked list is that a new contract is created for every node in the list. Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling'). However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function. As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.  This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds. Unfortunately, this is not universally true as shown by applying the same principle to the linked list with mapping.

Dequeuing in a linked list with mapping can be implemented in two ways. The simplest approach is to process a node, update the head pointer, and leave the `removed' node's data behind in the mapping untouched (where it will never be referenced again). Alternatively, we can call \texttt{DELETE} on each mapping entry once we are done processing a node in the PQ. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded---a net positive gas cost~\cite{wood2014ethereum}. As it can be seen in the last two rows of Table~\ref{tab:cleaning}, leaving the data on chain is cheaper than cleaning it up.

The lesson here is that gas refunds incentivize developers to clean up storage variables they will not use again, but it is highly contextual as to whether it will pay for itself. Further the cap on the maximum refund means that refunds are not fully received for large cleanup operations (however removing the cap impacts the miners' incentives to include the transaction). This is a complicated and under-explored area of Ethereum in the research literature. For our own work, we strive to be good citizens of Ethereum and clean up to the extent that we can---thus all PQs in Table~\ref{tab:PQUnitTests} implement some cleanup and we select linked list with mapping and \texttt{DELETE} for \cm.

@@

\cm is intended as a module that developers can modify as they choose---thus we tried to simplify the design at every step to make it highly extensible but still functional without any extensions. A call market will open for a specified period of time during which it will accept orders, and these orders are added to a PQ. Our vision (discussed below) is the market would be open for a very short period of time, close, and then reopen immediately (\eg every other block). We keep the design simple by not allowing cancellations. Because cancellations require a second transaction, and front-running attacks apply to cancellation orders~\cite{eskandari2019sok}.Also, markets are relatively short-lived and orders simply expire when the market call period ends.

@@

The main research question is how many orders can be processed in a single Ethereum transaction when closing the call market, using Ethereum today. As our previous experiments indicated, the choice of priority queue (PQ) implementation is the main influence on performance (see Table~\ref{tab:worst_case_matching}). We implemented a generic call market that interfaces with a generic PQ (at its own contract address) and ran experiments for each PQ implementation. We looked at the \textit{worst-case} for performance which is when every submitted bid and ask is marketable (\ie will require fulfillment). In the first two columns, we determined the highest number of orders that can be processed in a single call to the \texttt{closeMarket()} and not exceed the the current Ethereum block gas limit of 11,741,495. Since Ethereum will become more efficient over time, we also were interested in how much gas it would cost to execute 1000 pairs of orders which is given in the third column. The fourth column indicates the cost of submitting a bid or ask --- since this costs will vary depending on how many orders are already submitted (recall Figure~\ref{fig:random_insertion}), we average the cost of 200 order submissions.

@@

\paragraph{Code Security.} We used two security audit tools, \textit{Slither}\footnote{https://github.com/crytic/slither} and \textit{SmartCheck},\footnote{https://tool.smartdec.net} on \cm to find vulnerabilities and bad practices across 67 tests. \cm passes all tests except some `informational' warnings (\eg a costly loop) that are intentional design choices.

\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.

Potential for front-running still exists around ties on price and order cancellations (see below). Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them. In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a price improvement. A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price from their orders---and it removes any incentive to front-run these profits. For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.

@@

As a module, we try to keep \cm as simple as possible, and allow customizations and extensions as appropriate. We discuss potential modifications here.

@@

\subsection{Order Cancellations}

\cm does not support order cancellations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived. Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes). Finally, cancellations have a performance impact. Cancelled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

@@

A close alternative is to allow markets to open and close on different blocks. Specifically, the \texttt{closeMarket()} function calls \texttt{openMarket()} as a subroutine and sets two modifiers: orders are only accepted in the block immediately after the current block (\ie the block that executes the \texttt{closeMarket()}) and \texttt{closeMarket()} cannot be run again until two blocks after the current block.

@@

It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself. However we consider two other (more realistic) scenarios. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until there is no orders left in the list). Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. These fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).

@@

We implemented a variant of \cm using rollups on Arbitrum.\footnote{\url{https://offchainlabs.com} for more current details than the 2018 \textit{USENIX Security} paper~\cite{kalodner2018arbitrum}.} In this model, the token issuer (or other interested party) will run a dedicated server to watch Ethereum for function invocations submitted and sequenced on-chain, perform the function call off-chain, and write the resultant state on-chain. Anyone capable of running EVM code can verify the result. If it is incorrect, a dispute can be filed (with the correct state) and an on-chain correction will be made. With or without disputes, participants that validate the function calls for themselves can proceed knowing that the correct state will eventually be finalized.

@@

Our \cm variant is not the first rollup-based order book. Loopring 3.0\footnote{\url{https://loopring.org}} offers a continuous-time order book. The primary difference is that orders in Loopring 3.0 are submitted off-chain to the operator directly, whereas our variant requires on-chain submission. While on-chain submission is hampered by Ethereum's block limits, the threat model of reordering transactions is well-understood and our call market design mitigates most front-running attacks. In Loopring 3.0, the rollup proof does not ensure that the exchange did not reorder transactions, which is particularly problematic in a continuous-time order book. In short, we provide better protection against a malicious exchange while Loopring 3.0 provides even better performance.
